---
title: "Exploratory Analysis"
output: html_document
---

## Project title
Exploring the Users' Experience on Netflix.com

### Authors

Ronnie Chen: rchen24@uw.edu
Eric Kuo: ekuo0210@uw.edu
Gia An Nguyen: giaan01@uw.edu
Angela Li: angli03@uw.edu
Leo Ren:2319277580@qq.com &mengqr12@uw.edu

### Date

February 21, Winter 2022

### Abstract

We are concerned about how Netflix’s suggestion engine will allow the consumers to have a more viewer friendly experience, due to the rising popularity of this
streaming platform today. To address this concern, we plan to analyze user rating size in relation to rating to explore the influence of Rating level on user
rating score based on Netflix's search engines.

### Keywords

Algorithms, suggestion engines, Netflix, streaming platform

### Introduction  

In this project we decided to use a Kaggle dataset display Netflix shows and their ratings. Since the dataset incorporates Netflix’s suggestion engine into the
aggregated data, our group was thinking about exploring research questions relating to its impact and extension. As such we’d like to explore how Netflix’s
suggestion engine allow the consumers to have a more viewer friendly experience? How does their suggestion engine impact a show’s ratings and vice versa of how
does show’s ratings impact Netflix’s suggestion engine? Does release year have an impact on the suggestion engine? Do ratings make an impact on when Netflix
decides to stop hosting a show? The possibilities with this dataset are numerous. We chose this dataset because we wanted to work with a topic that was
entertaining and interesting but still prompting. I think that since we all have our personal experiences with Netflix, when working with this data, we are more
invested into our research and finding out the results since they have a direct relation to us as part of Netflix’s userbase. Furthermore, the impact of our
findings is substantial considering the scope of Netflix’s impact. Especially during the pandemic, their userbase has grown significantly when people searched for
entertainment options during lockdown. Since it also provides convenience from the comfort of your own home, I believe that any of our findings can make a
substantial impact.

### Related Work  

The possibilities of streaming has shifted our world through genres, labels and categories our daily media consumption. Netflix uses machine learning and
algorithms to break down its viewer's recommended shows and predicts other shows to keep their consumers interested. Take the trending Korean drama, Squid Game,
for example, how did this show become so popular on this streaming platform? While the Korean show has its personal labeled genre, it also contains "hyper-specific
categories" that are stored into "meta-data - the behind-the-scenes codes that support platforms like Spotify" (Beer). According to the Wired article, they gather
"what people watch, what they watch after, what they watch before, what they watched a year ago, what they've watched recently, and what time of day" and Netflix
combine this information "with more data aimed at understanding the content of the shows." This information from their viewers then gets categorized and analyzed
into multiple taste groups that are used for machine learning algorithms. This method is implemented all across the word. A research study conducted by Gomez-Uribe
and Neil Hunt indicated there is a collection of recommender algorithm that Netflix uses such as the personalized video ranker (PVR) and Top N video ranker
algorithm that catalogs videos for each member profile on the homepage of Netflix, or the video-video similarity algorithm for Netflix's Because You Watched (BYW)
recommendations. There are numerous algorithms implemented with Netflix's suggestion engines and with this project, we will dive into how exactly this huge
streaming platform recommends similar shows through its User Rating Score, Rating Description, Release Year, Title, and more complete the user's Netflix
experience.

### The Dataset

We found this dataset on the website Kaggle about Netflix shows. The dataset was created by a software engineer named Chase Willden. He completed his Masters of
Science at Boston University in data analytics. The data was collected because the author wanted to understand the distribution of the Netlfix show ratings as it
hasn't really been understood by anyone due to the large number of Netflix shows. Since gathering data for each show individually would take a very long time,
Chase collected the data by using the Netflix suggestion engine which allowed him to gather data for one show and those that are recommended based on the certain
selected show. There are 496 unique rows in this dataset with seven columns that contains strings, integers, and decimals. Some possible limitations or problems
with this data is that the ratings are completely based on Netflix users which doesn't necessarily represent the entire population of people who watch the shows.
There are people who could possibly watch the shows on TV without Netflix or even pirate them which means that the data isn't necessarily accurate to the entire
population. There are also people won't don't necessarily have access to Netflix meaning that the data can only represent a certain population without making
assumptions about what some people "would like".

### Implications

We found this dataset on the website Kaggle about Netflix shows. The dataset was created by a software engineer named Chase Willden. He completed his Masters of
Science at Boston University in data analytics. The data was collected because the author wanted to understand the distribution of the Netlfix show ratings as it
hasn't really been understood by anyone due to the large number of Netflix shows. Since gathering data for each show individually would take a very long time,
Chase collected the data by using the Netflix suggestion engine which allowed him to gather data for one show and those that are recommended based on the certain
selected show. There are 496 unique rows in this dataset with seven columns that contains strings, integers, and decimals. Some possible limitations or problems
with this data is that the ratings are completely based on Netflix users which doesn't necessarily represent the entire population of people who watch the shows.
There are people who could possibly watch the shows on TV without Netflix or even pirate them which means that the data isn't necessarily accurate to the entire
population. There are also people won't don't necessarily have access to Netflix meaning that the data can only represent a certain population without making
assumptions about what some people "would like".

### Limitations & Challenges

While doing research, we might run into challenges with misinformation and biased resources. Because Netflix has millions of subscribers that watch a variety of
shows, it would be challenging for us to analyze how interactions with Netflix can alter the preferences. Moreover, the designated factors such as rating that
could impact the interests limit our ability to better understand what is the main influencer to these recommendations. There are also data limitations in which
the data can not represent all subscribers, this will create bias in our findings. The time of a day, devices, and duration are some of the existing data to be
used as inputs for Netflix to process in their algorithms, but duration might not be accurate especially if one kept playing shows without watching. We need to
address more broadly the accuracy of data and view it more holistically.

### Summary Information

Write a summary paragraph of findings that includes the 5 values calculated from your summary information R script

```
data <- read_csv("https://raw.githubusercontent.com/info-201b-wi22/exploratory-analysis-MiniPasta/main/archive/netflix_titles.csv?token=GHSAT0AAAAAABQJQPQGV54RWO526HV327CWYQ3FKJQ")
summary_info <- list()
summary_info$num_movies <- data %>%
  group_by(type == 'Movies') %>%
  summarise(count=n())
summary_info$num_tv <- data %>%
  group_by(type == 'TV Show') %>%
  summarise(count=n())
summary_info$num_directors <- data %>%
  filter(type=="Directors") %>% group_by(director) %>% summarise(count=n())
summary_info$num_country <- data %>%
  filter(type=="Movie") %>% group_by(director) %>% summarise(count=n())
  summary_info$max_country <- data %>%
  filter (country == max(country, na.rm == TRUE))
  %>% pul1 (country)

View(summary_info)
```



### Table

Include a table of aggregate information

Describe why you included the table and what information it reveals

### Chart 1
What are the top 10 directors with the largest number of movies?
```{r, echo = FALSE, warning=F, message=F, code = readLines ("chart1.R")}
print(test)
```
The bar plot tells us that Rajiv Chilaka has directed the largest number of movies, the number is 19, Raúl Campos, Jan Suter has directed the second largest number
of movies, the number if 18, Suhas Kadav has directed the third largest number of movies, the number is 16.



### Chart 2

```{r, echo = FALSE, warning=F, message=F, code = readLines ("chart2.R")}
print(test2)
```

We chose this chart in order to  see all the types of ratings that exists in Netflix's streaming service and also compare it to the release year of that show or
movie. This furthermore reveals a history of the industrial discourses surrounding Netflix's audience data and concludes the discussion of streaming audience data
that situates in the emerging's realities of "popular" television in the context the medium's broader transformation and continuities.

### Chart 3

```{r, echo = FALSE, warning=F, message=F, code = readLines ("chart3.R")}
print(test3)
```

Describe why you chose this chart and what information it reveals
